---
title: "tagMeppr"
author: "Robin H. van der Weide"
date: "`r Sys.Date()`"
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

TRAVIS <- !identical(tolower(Sys.getenv("TRAVIS")), "true")
knitr::opts_chunk$set(purl = TRAVIS)

```


```{r logo, eval = TRAVIS, out.width = "25%", fig.align = 'center', echo = F, fig.path="vignettes"}
knitr::include_graphics("logo_tagMeppr.pdf")
```

Hi there! Welcome! 

```{r lib, eval = F}
library(tagMeppr)
```

# A hybrid reference genome 
Remember: you only have to make a tagMepprIndex once per genome and protocol! 
This means that you can use it for however many samples for that protocol and 
organism (e.g. PiggyBac in human cells) you may have.

```{r makeIndex, eval = F}
library("BSgenome.Hsapiens.UCSC.hg19")

reference_hg19_PB = makeIndex(indexPath = '.', 
                              bsgenome = "BSgenome.Hsapiens.UCSC.hg19", 
                              ITR = 'PiggyBac', 
                              targetInsertionSite = 'TTAA')
```

Loading a tagMepprIndex is easy with loadIndex().

```{r loadIndex, eval=T, cache=T, cache.lazy=F}
reference_hg19_PB = loadIndex('BSgenome.Hsapiens.UCSC.hg19_PiggyBac_tagMeppRindex.fa.gz')
```

You can use print() on this tagMepprIndex, which gives you a lot of information: 
```{r, eval=T, cache=F, cache.lazy=F}
print(reference_hg19_PB)
```

# The tagMepprSample-object

## Creating a new sample

```{r newTagMeppr, eval=T, cache=T, cache.lazy=F}
C91 = newTagMeppr(F1 = 'clone91_FWD_R1.fq.gz',
                 F2 = 'clone91_FWD_R2.fq.gz',
                 R1 = 'clone91_REV_R1.fq.gz',
                 R2 = 'clone91_REV_R2.fq.gz',
                 name = "clone9 (minimised)",
                 protocol = 'PiggyBac')
```

This is the print:
```{r, eval=T, cache=T, cache.lazy=F}
print(C91)
```

# Aligning
Omg. Mapping without leaving R! Please check if you have BWA and samtools intalled.
Note no <- signs

```{r align, eval=T, cache=T, cache.lazy=F, message=FALSE,results='hide'}
align(exp = C91, 
      ref = reference_hg19_PB, 
      cores = 30, 
      empericalCentre = T)
```



The object will be updated, which keeps your evironment tidy.
```{r, eval=T, cache=T, cache.lazy=F}
print(C91)
```

# Find insertions

```{r FI, eval=T, cache=T, cache.lazy=F}
findInsertions(C91, reference_hg19_PB)
```

```{r, eval=T, cache=T, cache.lazy=F}
print(C91)
```

# Plot

```{r PI, eval=T, cache=T, cache.lazy=F, fig.height= 4, fig.width=6.7}
plotInsertions(exp = C91)
```


## Plot muliple samples

```{r makeList, eval=T, echo = F, cache=T, cache.lazy=F}
C91_a = C91
C91_b = C91

C91_a$name = 'clone9 subset 1'
C91_b$name = 'clone9 subset 2'

C91_a$results = sample(C91_a$results, size = floor(length(C91_a$results)/2))
C91_b$results = sample(C91_b$results, size = floor(length(C91_b$results)/2))

tagMepprSampleList = list(C91_a, C91_b)
```


```{r PImult1, eval=T, cache=T, cache.lazy=F, fig.height= 4, fig.width=6.7}
plotInsertions(tagMepprSampleList, sideBySide = F)
```


```{r PImult2, eval=T, cache=T, cache.lazy=F, fig.height= 4, fig.width=6.7}
plotInsertions(tagMepprSampleList, sideBySide = T)
```
